---
title: "Lab-Submission-Markdown.Rmd"
author: "Wisdom"
date: "2023-10-27"
output:
  github_document:
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |     |
|----------------------------------------------|-----|
| **Student ID Number**                        | ... |
| **Student Name**                             | ... |
| **BBIT 4.2 Group**                           | .WISDOM.. |
| **BI Project Group Name/ID (if applicable)** | ... |

# Setup Chunk
## ggplot2 ----
## caret ----
## mlbench ----
```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

```{r}
if (require("ggplot2")) {
  require("ggplot2")
} else {
  install.packages("ggplot2", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
if (require("caret")) {
  require("caret")
} else {
  install.packages("caret", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
if (require("mlbench")) {
  require("mlbench")
} else {
  install.packages("mlbench", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
if (require("pROC")) {
  require("pROC")
} else {
  install.packages("pROC", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

```

## STEP 2. Load the Datasets ----

### The Boston Housing Dataset ----
# Execute the following to load the “BostonHousing” dataset which is offered
# in the "mlbench" package:
```{r}
data("BostonHousing")
```

## 1.b. Determine the Baseline Accuracy ----
  # Identify the number of instances that belong to each class (distribution or
  # class breakdown).
  
  # The result should show that 65% tested negative and 34% tested positive
  # for diabetes.

```{r}
data("BostonHousing")
boston_housing_medv <- BostonHousing$medv
cbind(frequency = table(boston_housing_medv),
      percentage = prop.table(table(boston_housing_medv)) * 100)
```
## 1.c. Split the dataset ----
# Define a 75:25 train:test data split of the dataset.
# That is, 75% of the original data will be used to train the model and
# 25% of the original data will be used to test the model.
# Define a 75:25 train-test split
```{r}
set.seed(123)  # For reproducibility
train_index <- createDataPartition(BostonHousing$medv,
                                   p = 0.75,
                                   list = FALSE)
boston_housing_train <- BostonHousing[train_index, ]
boston_housing_test <- BostonHousing[-train_index, ]
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
